---
title: "Weekly exercise 3"
output: 
  learnr::tutorial:
    theme: "sandstone"
    css: css/styles.css
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library("learnr")
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Question 7 a)

Suppose $G\sim\text{Geom}(1/4)$. The following code generates $101$ simulated values of $G$ and stores them in the ascending order in vector `sims`. `base_plot` is a `ggplot` object plotting `sims_plot` along the x-axis as black points and segments in dark grey representing the distance from each value to the expectation. In the provided code space below, the variables `N`, `theta`, `sims`, and `sims_plot` are readily available.

```{r q7a-setup, echo=TRUE}
library(ggplot2)
set.seed(123)
N <- 101
theta <- 1/4
sims <- sort(rgeom(N, theta) + 1)
sims_plot <- ggplot(mapping = aes(x = seq_len(N), y = sims)) +
  theme_classic() +
  geom_segment(aes(xend = seq_len(N), yend = 1 / theta), 
               color = "darkgrey", linewidth = 1) +
  geom_point(size = 2)  +
  labs(x = "Cumulative count", y = "Simulated value") +
  scale_x_continuous(breaks = c(1, 26, 51, 76, 101)) +
  scale_y_continuous(
    breaks = c(range(sims), median(sims), 1 / theta)
  ) 
```

```{r q7a, exercise=TRUE, exercise.lines=30}
# i. Compute median of G.
# ii. Add annotation layers
sims_plot
# iii. Count simulated points strictly above and strictly below the horizontal red dotted line.
# iv. Sum the lengths of grey bars above and below the orange dashed line.
```

iii. Are the counts the same? Explain why they are or they are not the same.

```{r}
shiny::textAreaInput(
  "q7a-iii", "You can type your answer here", width = "100%",height = "120px")
```


iv. Based on the two values, what is the estimated mean of $G - E[G]$?

```{r echo=FALSE}
shiny::textAreaInput(
  "q7a-iv", "You can type your answer here", width = "100%",height = "120px")
```

## Question 7 b)

Recall Michael's bike travel plan from Question 1. Let $B$ be the distance in kilometers until he experiences a mechanical failure with his bike when he chooses between the "normal" and the "hard" terrains with a coin flip. Use $100,000$ simulations to estimate $E[B]$ and $\text{Var}(B)$^[If you were not able to compute $\lambda_H$, you may use $\lambda_H = 1/60$].


```{r q7b, exercise=TRUE, exercise.lines=30}
N <- 10^5
```


## Question 7 c)

Consider the unit circle, or a circle with radius of 1. Let $X\sim\text{U}(-1,1)$. Suppose an arc is drawn by connecting the top and bottom intersections of the vertical line at $X$ and the unit circle. Let $L$ be the length of the arc connecting the intersections from the right. 

Simulate 100,000 samples of $L$, create a density histogram of the simulated values, and compute $P(L < 4)$.

```{r q7c, exercise=TRUE, exercise.lines=30}
N <- 10^5
L # simulate L
# estimate the probability
# create the density histogram
ggplot(mapping = aes(x = L)) +
  theme_minimal() 
```

```{r q7c-hint-1}
# check
?sin

```

```{r q7c-hint-2}
# (Optional) if you want to color bars that represent regions where L < 4.
# You can color bars based on a condition mapped inside aes().
x <- rpois(100, 3)
y <- rgeom(100, .3)
ggplot() +
  theme_void() +
  geom_bar(aes(x = x, y = y, fill = x >3), stat = "identity")
```

